\documentclass[11pt,a4paper]{article}

% --- Page layout (minimum required) ---
\usepackage[a4paper,margin=2cm]{geometry}
\usepackage{setspace}
\setstretch{1.0} % single (or greater)

% --- Times-based font ---
\usepackage{newtxtext}
\usepackage{newtxmath}

% --- Useful basics ---
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{latexsym}
\usepackage{tabularx}

% --- Tidy lists ---
\usepackage{enumitem}
\setlist{nosep}

% --- Header/footer (simple page number for applicant self-check) ---
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\lhead{Applicant's last name}
\chead{Curriculum vitae and Track Record}
\rhead{Project acronym}  
\cfoot{\thepage}

% ============================================================
% Guidance toggle (recommended)
%   - Keep \guidancetrue while drafting.
%   - Switch to \guidancefalse for the final PDF (hides notes/prompts).
% ============================================================
\newif\ifguidance
\guidancetrue
% \guidancefalse

% --- Helper: HARD LIMIT box (draft mode only) ---
\newcommand{\HardLimitBox}{%
\ifguidance
\vspace*{-0.25\baselineskip}
\begin{center}
\fbox{%
\begin{minipage}{0.96\linewidth}
\small
\textbf{Hard limits (submission rules):}
\begin{itemize}
  \item Max \textbf{4 pages} total.
  \item Formatting: \textbf{A4, \(\ge\)11 pt, margins \(\ge\)2 cm, single spacing or greater}.
\end{itemize}
\noindent \textbf{Note:}
\begin{itemize}
\item You may modify this template if necessary.
\item Practical tip: Draft with \texttt{\textbackslash guidancetrue}, finalize with  \texttt{\textbackslash guidancefalse}.
\end{itemize}
\end{minipage}}
\end{center}
\vspace*{0.5\baselineskip}
\fi
}

\newcommand{\hint}[1]{\ifguidance{\noindent\color{gray}\small #1}\par\fi}

\begin{document}

\HardLimitBox

\section*{Personal details}

\begin{description}
\item[Family name, First name:]

\item[Researcher unique identifier(s) (ORCID, Research ID, etc.):]

\item[URL for web site:]
\end{description}

\subsection*{Education and key qualifications}

\begin{tabularx}{\linewidth}{@{}lX@{}}
\textbf{DD/MM/YYYY} & \textbf{Ph.D.}\\
& Name of Faculty/ Department, Name of University/ Institution, Country\\
& Name of Ph.D. Supervisor\\[4pt]
\textbf{YYYY} & \textbf{Master}\\
& Name of Faculty/ Department, Name of University/ Institution, Country\\
\end{tabularx}

\subsection*{Current position(s)}

\begin{tabularx}{\linewidth}{@{}lX@{}}
\textbf{YYYY -- YYYY} & \textbf{Current Position}\\
& Name of Faculty/ Department, Name of University/ Institution, Country\\[4pt]
\textbf{YYYY -- YYYY} & \textbf{Current Position}\\
& Name of Faculty/ Department, Name of University/ Institution, Country\\
\end{tabularx}

\subsection*{Previous position(s)}

\begin{tabularx}{\linewidth}{@{}lX@{}}
\textbf{YYYY -- YYYY} & \textbf{Position held}\\
& Name of Faculty/ Department, Name of University/ Institution, Country\\[4pt]
\textbf{YYYY -- YYYY} & \textbf{Position held}\\
& Name of Faculty/ Department, Name of University/ Institution, Country\\
\end{tabularx}


\section*{Research achievements and peer recognition}

\subsection*{Research achievements}

\hint{Provide up to ten research outputs demonstrating how you advanced knowledge in your field (emphasise recent achievements). Outputs may include publications, preprints, books/chapters, proceedings, data sets, software, patents/licenses, standards, start-ups, or other relevant outputs. Optionally add brief factual notes on significance and your role.}

\begin{enumerate}[leftmargin=*,itemsep=4pt]
  \item Output 1 -- bibliographic entry / description.\\
        \hint{Optional: short factual note on significance and your role.}
  \item Output 2 -- bibliographic entry / description.\\
        \hint{Optional: short factual note.}
\end{enumerate}

\subsection*{Peer recognition}

\hint{List selected examples of significant recognition (if applicable): prizes/awards, fellowships, elected memberships, invited presentations, etc. Optionally add a short significance note.}

\begin{itemize}[leftmargin=*,itemsep=3pt]
  \item Prize / award / fellowship / membership / invited talk, year\\
  \hint{Optional: short significance note.}
  % \item \textit{Another item}
\end{itemize}

\section*{Additional information}

\hint{You may provide additional information to give context to the evaluation panels when assessing your achievements and recognition.}

\subsection*{Career breaks, diverse career paths and major life events}

\hint{Short factual explanation of career breaks or diverse paths (e.g., secondments, part-time work, time in other sectors), major life events (e.g., long-term illness), or pandemic-related constraints affecting research productivity.}

\subsection*{Other contributions to the research community}

\hint{List noteworthy contributions beyond research outputs and peer recognition (e.g., reviewing/editorship, committee work, mentoring, leadership roles) with short explanations.}

\begin{itemize}[leftmargin=*,itemsep=3pt]
  \item Contribution\\
  \hint{Optional: short explanation.}
\end{itemize}

\end{document}
